---
title: "Assignment#7"
format: html
editor: visual
---

## Approach

This assignment is designed to give experience with HTML and JSON file formats and for this assignment we are supposed to use 3 books and their information. I will decide on the books in my approach and manually create the raw HTML file and JSON file. Ill use these 3 books on the topic of strength training and powerlifting.

1.  Starting Strength by Mark Rippetoe. Year: 2011. Publisher: Aasgaard Company. Genre: Fitness.
2.  Practical Programming for Strength Training by Mark Rippetoe and Andy Baker. Year: 2013. Publisher: Aasgaard Company. Genre: Strength Training
3.  The New Encylopedia of Modern Bodybuilding by Arnold Schwarzenegger and Bill Dobbins. Year: 1998. Publisher: Simon & Schuster. Genre: Bodybuilding

## Code Base 

```{r}
html_content <- '<!DOCTYPE html>
<html>
  <head><title>Books</title></head>
  <body>
    <table>
      <thead>
        <tr>
          <th>Title</th><th>Authors</th><th>Year</th><th>Publisher</th><th>Genre</th>
        </tr>
      </thead>
      <tbody>
        <tr>
          <td>Starting Strength</td>
          <td>Mark Rippetoe</td>
          <td>2011</td>
          <td>Aasgaard Company</td>
          <td>Fitness</td>
        </tr>
        <tr>
          <td>Practical Programming for Strength Training</td>
          <td>Mark Rippetoe, Andy Baker</td>
          <td>2013</td>
          <td>Aasgaard Company</td>
          <td>Strength Training</td>
        </tr>
        <tr>
          <td>The New Encyclopedia of Modern Bodybuilding</td>
          <td>Arnold Schwarzenegger, Bill Dobbins</td>
          <td>1998</td>
          <td>Simon &amp; Schuster</td>
          <td>Bodybuilding</td>
        </tr>
      </tbody>
    </table>
  </body>
</html>'

writeLines(html_content, "books.html")

json_content <- '{
  "books": [
    {
      "title": "Starting Strength",
      "authors": "Mark Rippetoe",
      "year": 2011,
      "publisher": "Aasgaard Company",
      "genre": "Fitness"
    },
    {
      "title": "Practical Programming for Strength Training",
      "authors": "Mark Rippetoe, Andy Baker",
      "year": 2013,
      "publisher": "Aasgaard Company",
      "genre": "Strength Training"
    },
    {
      "title": "The New Encyclopedia of Modern Bodybuilding",
      "authors": "Arnold Schwarzenegger, Bill Dobbins",
      "year": 1998,
      "publisher": "Simon & Schuster",
      "genre": "Bodybuilding"
    }
  ]
}'

writeLines(json_content, "books.json")

```

```{r}

library(rvest)
```

### Load HTML into dataframe 

```{r}
df_html <- read_html("books.html") |>
  html_element("table") |>
  html_table()

colnames(df_html) <- tolower(colnames(df_html))

df_html
```

### Load JSON into a data frame 

```{r}
library(jsonlite)
```

```{r}
df_json <- fromJSON("books.json")$books
df_json$year <- as.integer(df_json$year)

df_json
```

### Compare the 2 dataframes 

```{r}
library(dplyr)

df_json <- df_json[, colnames(df_html)]

# Are they identical?
identical(df_html, df_json)

# What differs (if anything)?
all.equal(df_html, df_json)

# Side by side
bind_rows(
  mutate(df_html, source = "HTML"),
  mutate(df_json, source = "JSON")
)
```
